\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2019-05-23 paper/manuscript_paNote.tex
added table for pipeline

A local government's website is an important source of information about policies and procedures for residents, community stakeholders and scholars. Existing research in public administration, public policy, and political science has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis. We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content. Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information. We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States. We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website. Using a structural topic model, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity and fire safety.
%\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots. Snapshots of websites before and after transitions of power are acquired through the Wayback Machine. We apply statistical topic models based in latent dirichlet allocation, focusing on changes to the websites. We present results on both which topics see the greatest degree of change associated with transitions in city administrations, and how the topics modified differ with regard to political parties.

@@

To this end, we turn to to an approach that is much more common in natural langauge processing than political methodology -- part-of-speech (POS) tagging and named entity recognition (NER). While not their original purpose, these procedures perform very well in separating the wheat from the chaff. As names convey no substantive information, we NER is used to detect to remove them.\footnote{We retain laws, nationalities or religious or political groups (which are politically salient with respect to immigration and identity) as well as works of art (which frequently feature statutes, plans, etc.)} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, adjectives. Furthermore, we keep proper nouns that also occur as nouns -- this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name. Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word. For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''. Thus, lemmatization makes the results more easily comprehensible.} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyR}. This parsing-based approach is very effective in distilling a comparable corpus from a varied set of sources, as the grammatical rules of the English language remain their common denominator. To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell})\footnote{As we are using \texttt{spacyR} with an English parser, non-English words tend to be erroneously categorized as (proper) nouns.}.

@@

After all the preprocessing is set and done, our corpus consists of 259,099 documents.  In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data. The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package.

\begin{table}[ht]
    \centering
    \begin{tabular}{lrr}
        \hline
        Process & Software & gov2text \\
        \hline
        1. Assemble url list. & N/A & no \\
        2. Collect website files. & wget \& Selenium & no \\
        3.  & & \\
        \hline
    \end{tabular}
    \caption{\label{tab:list} Data collection and processing pipeline.} 
\end{table}

@@

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis. Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government. We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.

>>>>

A local government's website is an important source of information about policies and procedures for residents, community stakeholders and scholars. Existing research in public administration, public policy, and political science has relied on manual methods of website content collection and processing, limiting the scale and scope of website content analysis. We develop a methodological pipeline that researchers can follow in order to gather, process, and analyze website content. Our approach, which represents a considerable improvement in scalability, involves downloading the entire contents of a website, extracting the text and discarding redundant information. We provide an R package that can be used to apply our proposed pipeline. We illustrate our methodological pipeline through the collection and analysis of a new and innovative dataset---the websites of over two hundred municipal governments in the United States. We build upon recent research that analyzes how variation in the partisan control of government relates to content made available on the government's website. Using a structural topic model, we find that cities with Democratic mayors provide more information on policy deliberation and crime control, whereas Republicans prioritize basic utilities and services such as water, electricity and fire safety.
%\noindent We explore the effect of transitions of power in municipal governments on the content of their websites. We hypothesize that when party control changes, city administrators modify the contents of their websites in order to fit the agenda of the new incumbent. To test this theory, we study cities in Indiana and Louisiana, two states in which all municipal elections are partisan and the parties of the candidates appear on the ballots. Snapshots of websites before and after transitions of power are acquired through the Wayback Machine. We apply statistical topic models based in latent dirichlet allocation, focusing on changes to the websites. We present results on both which topics see the greatest degree of change associated with transitions in city administrations, and how the topics modified differ with regard to political parties.

@@

To this end, we turn to a common method in natural langauge processing---part-of-speech (POS) tagging and named entity recognition (NER). While not their original purpose, these procedures perform very well in separating the wheat from the chaff. As names convey no substantive information, NER is used to detect and remove them.\footnote{We retain laws, nationalities or religious or political groups (which are politically salient with respect to immigration and identity) as well as works of art (which frequently feature statutes, plans, etc.)} Furthermore, we select words on the basis of their POS-tags, retaining only nouns (by far the most informative category), verbs, and adjectives. Furthermore, we keep proper nouns that also occur as nouns---this removes names, but retains titles such as ``Police Chief'' which can appear as proper nouns if they are followed by a name. Finally, we also conduct lemmatization to reduce words to their basic form.\footnote{Lemmatization is similar to stemming, but works in a somewhat more sophisticated manner by taking grammar and surrounding words into account to identify the dictionary form of a word. For example, the lemma of the word ``lemmatization'' would be ``lemmatize'', whereas most stemmers would simply chop off the ending, which would yield ``lemmatiz''. Thus, lemmatization makes the results more easily comprehensible.} POS-tagging, NER and lemmatization are all implemented through \texttt{spacyR}. This parsing-based approach is very effective in distilling a comparable corpus from a varied set of sources, as the grammatical rules of the English language remain their common denominator. To deal with any leftover issues, we remove words with less than three characters (these are usually artifacts from improperly encoded documents and faulty or impartial optical character recognition), stopwords and non-English words (using the R package \texttt{Hunspell})\footnote{As we are using \texttt{spacyR} with an English parser, non-English words tend to be erroneously categorized as (proper) nouns.}.

@@

After all the preprocessing is set and done, our corpus consists of 259,099 documents.  In Table \ref{tab:list} we summarize all of the steps we take in gathering and processing our data. The summary includes a brief description of the step, the software packages used, and an indicator of whether the method is implemented in our R package, \texttt{gov2text}.

\begin{table}[ht]
    \centering
    \begin{tabular}{lrr}
        \hline
        Process & Software dependency & \texttt{gov2text} inclusion \\
        \hline
        1. Assemble url list. & N/A & no \\
        2. Collect website files. & wget \& Selenium & no \\
        3. Remove names. & \texttt{spacyR} & yes \\
        4. Retain nouns, verbs, adjectives. & \texttt{spacyR} & yes \\
        5. Lemmatize text. & \texttt{spacyR} & yes \\
        6. Retain tokens that are English words. & \texttt{Hunspell} & yes \\
        7. Convert corpus to document-term matrix. & [MARKUS?] & no \\
        \hline
    \end{tabular}
    \caption{\label{tab:list} Data collection and processing pipeline. Steps to collect and prepare text for topic modeling.} 
\end{table}

@@

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. We have produced an R package \texttt{gov2text}, in which we have implemented and wrapped the core components of our pipeline. This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis. Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government. We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.
